\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-10-29 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Edits in Sections 2 and 3

\section{Spatial Discretization}\label{se:SpacialDiscretization}
Here we use the finite-volume/first-order discontinuous Galerkin method to illustrate how the closure affects the realizability-preserving property of the scheme.
To simply the illustration, let's focus on one-dimension uniform mesh on Cartesian coordinates.
We divide the spatial domain $D$ evenly into $N$ cells and denote the $i$th cell as $\bK_{i}$ with $i = 1,\ldots,N$, so that
\begin{equation*}
D = \cup_{i = 1}^{N} \bK_{i} \quad \text{with} \quad
  \bK_{i}=\{\,x : x\in(x_{i-1/2}, x_{i+1/2})\}.
\end{equation*}
Each of the cells has a length, $|\dx|$ and $|\dx| = D/N = \int_{\bK}d\vect{x}$.
The cell-average moments:
\begin{equation}
\bcM_{i} = \dfrac{1}{|\dx|} \int_{\bK_i}\bcM dx.
\end{equation}
Integrating Eq.~\eqref{eq:momentEquations} for each cell $\bK_{i}$ given
\begin{equation}
\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{|\dx|} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
\label{eq:SemiDiscretizatedMomentEquation}
\end{equation}
where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
In this paper we use the simple Lax-Friedrichs flux, given by
\begin{equation}
  \widehat{\bcF}_{LF}(\vect{\cM}_{a},\vect{\cM}_{b})
  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
  \label{eq:Lax-Friedrichs flux}
\end{equation}
Therefore, by treating the flux term explicitly and the collision term implicitly, we have
\begin{align}
\bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i}),
\label{eq:MomentIMEX}
\end{align}
where we define
\begin{align}
\widetilde{\bcM}^{n}_{i} 
& = \bcM_{i}^{n} - \dfrac{\dt}{|\dx|} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
& = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right],
\label{eq:widetildeM}
\end{align}
and $\beta := \frac{\dt}{|\dx|}$.

>>>>

\section{Spatial Discretization}\label{se:SpacialDiscretization}

In this section we discretize the two-moment model with a simple first-order finite volume method to illustrate how the closure affects the realizability-preserving property of the scheme.  
By assuming that the moments at time level $t^{n}$ ($\bcM^{n}$) satisfy the bounds in Eq.~\eqref{eq:MomentsBounds}, our goal is to identify sufficient conditions such that the moments at time level $t^{n+1}$ ($\bcM^{n+1}$) also satisfy the bounds.  
To simply the illustration, we limit the discussion to one spatial dimension and employ a uniform Cartesian mesh.  
(The extension to multiple spatial dimensions and high-order discretization using the discontinuous Galerkin method is given in \cite{chu_etal_2018})

We divide the spatial domain $D$ into $N$ uniform cells and denote the $i$-th cell by $\bK_{i}$, with $i = 1,\ldots,N$; i.e.,
\begin{equation*}
  D = \cup_{i = 1}^{N} \bK_{i} \quad \text{with} \quad
  \bK_{i}=\{\,x : x\in(x_{i-1/2}, x_{i+1/2})\}.
\end{equation*}
Denote the cell width by $\dx = D/N$.  
The cell-average of the moments is defined as
\begin{equation}
  \bcM_{i} = \dfrac{1}{\dx} \int_{\bK_i}\bcM dx.
\end{equation}
Integrating Eq.~\eqref{eq:momentEquations} over $\bK_{i}$ gives
\begin{equation}
  \dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
  \label{eq:SemiDiscretizatedMomentEquation}
\end{equation}
where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the collision term evaluated with $\bcM_{i}$.
In this paper we use the global Lax-Friedrichs flux (setting the largest absolute eigenvalue of the flux Jacobian to one)
\begin{equation}
  \widehat{\bcF}_{\LF}(\vect{\cM}_{a},\vect{\cM}_{b})
  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
  \label{eq:Lax-Friedrichs flux}
\end{equation}
By treating the transport term explicitly with forward Euler and the collision term implicitly with backward Euler, we have
\begin{align}
  \bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i}),
  \label{eq:MomentIMEX}
\end{align}
where we have defined
\begin{align}
  \widetilde{\bcM}^{n}_{i} 
  & = \bcM_{i}^{n} - \frac{\dt}{\dx} \left( \widehat{\bcF}_{\LF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}_{\LF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
  & = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right],
\label{eq:widetildeM}
\end{align}
and $\beta = \frac{\dt}{\dx}$.

### 2018-10-29 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated Astronum_2018.
Edits in Sections 2 and 3

\subsection{Transport Equations}
Consider neutrino transport through static dense matter with only emission, absorption and isotropic iso-energetic scattering.
The Boltzmann equation after scaling to dimensionless units ($k_{B} = c = 1$) can be written as
\begin{equation}
  \pd{f}{t}+\vect{\ell}\cdot\nabla f
  =\f{1}{\tau}\,\cC(f).
  \label{eq:boltzmann}
\end{equation}
The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.  
$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
On the right-hand side, $\tau$ is collision time scale: $\tau\ll1$ for opaque regions where neutrinos have frequent interactions with the background; $\tau\gg1$ for transparent regions where neutrinos rarely interact with the background and stream freely.
$\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
\begin{equation}
  \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega-f\,\big),
  \label{eq:collisionTerm}
\end{equation}
with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$ corresponding to pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$ corresponding to pure scattering. 
$f_{0}$ is the neutrino equilibrium distribution function, which has the following form:
\begin{equation}
  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}.
  \label{eq:fermiDirac}
\end{equation}
$T(\vect{x})$ is the temperature in energy units and $\mu(\vect{x})$ is the neutrino chemical potential.
Both of them depend on the properties of the background as a function of $\vect{x}$.

\subsection{Two-Moment Model}
An approximate solution of the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by employing a two-moment model.
Define the angular moments of the distribution function as follows
\begin{equation}
  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
  \label{eq:angularMoments}
\end{equation}
where $\vect{z}:=\{\varepsilon,\vect{x}\}$.
The zeroth moment, $\cJ$, is referred to as the particle density.
The first moment, $\bcH$, is the particle flux, and the second moment, $\bcK$, is the stress tensor.
We can integrate Eq.~\eqref{eq:boltzmann} to obtain equations for the zeroth and the first moments
\begin{equation}
  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
  \label{eq:momentEquations}
\end{equation}
with $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, and
\begin{equation}
  \vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM},
  \label{eq:collisionTermMoments}
\end{equation}
where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$, $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, and
$\vect{I}$ is the identity matrix.
Therefore, solving the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, for the neutrino distribution function, $f(\omega,\vect{z},t)$, is approximated by solving the two-moment equations for the neutrino number density, $\cJ(\vect{z},t)$, and flux, $\bcH(\vect{z},t)$.

\subsection{Algebraic Closures }
As is shown in the previous section, the moment equation for $\bcH$ involves $\bcK$ and the two-moment system is open. 
To close the two-moment system, an algebraic closure is constructed.
For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as follows:
\begin{equation}
\bcK = \vect{k} \cJ,
\end{equation}
where $\vect{k}$ is the Eddington tensor.
For example, assuming the neutrino distribution is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
\begin{equation}
  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
  \label{eq:eddingtonTensor}
\end{equation}
where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.

\subsection{Constraints on the Moments}
Neutrinos are fermions, and obey the Pauli exclusion principle, i.e. $f \in [0,1]$.
As a result, the angular moments of $f$ and the Eddington factor $\chi$ are constrained as follows\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}: 
\begin{align}
\cJ \in[0,1], \quad &(1-\cJ)\cJ-|\vect{\cH}| \geq 0, \label{eq:MomentsBounds}\\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  \leq & \chi \leq \min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
  \label{eq:eddingtonFactorBounds}
\end{align}
where $h = |\bcH|/\cJ$ is the flux factor.

The constraints in Eq.~\eqref{eq:MomentsBounds} define realizable $\bcM$, which define a convex set in the $\cJ$-$\bcH$ space.
As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spatial discretization possible.

The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve more attention than has been given.
They have equal importance relative to the inequalities in Eq.~\eqref{eq:MomentsBounds} in maintain consistency with respect to Fermi-Dirac statistics.
The Eddington factor given by the algebraic closures discussed in \cite{murchikova_etal_2017} are examined in this paper as examples.
We consider various occupancies and plot $\cJ = 0.1$ and $\cJ = 0.9$ as examples for low and high occupancy, respectively, in Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure}.
As the figure shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
The only algebraic closure that remains within the Eddington factor bounds among those plotted is Cernohorsky and Bludman's \cite{cernohorskyBludman_1994}.
Though Levermore closure and Minerbo closure don't conserve the bounds in the high occupancy limit, they are widely used: {O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} use Minerbo closure, and Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016} use Levermore clsoure.
\rc{Add more discussion.}

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupancy) and $\cJ=0.9$ (right panel, high occupancy).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dashed black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

>>>>

\subsection{Transport Equations}

We consider neutrino transport through a static background, and include neutrino-matter interactions due to emission, absorption, and isotropic iso-energetic scattering.  
After scaling to dimensionless units, the Boltzmann equation can be written as
\begin{equation}
  \pd{f}{t}+\vect{\ell}\cdot\nabla f
  =\f{1}{\tau}\,\cC(f),
  \label{eq:boltzmann}
\end{equation}
where the distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.  
$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
On the right-hand side, $\tau$ is collision time scale.  
In opaque regions, where neutrinos have frequent interactions with the background, $\tau\ll1$.  
In transparent regions, where neutrinos rarely interact and stream freely, $\tau\gg1$.
The collision term, $\cC(f)$, which models emission, absorption, and isotropic and elastic scattering is given by
\begin{equation}
  \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega-f\,\big),
  \label{eq:collisionTerm}
\end{equation}
where $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$ is the ratio of the absorption opacity $\sigma_{\Ab}$ to the total opacity.  
The scattering opacity is $\sigma_{\Scatt}$.  
The limit $\xi = 1$, when $\sigma_{\Scatt} = 0$, corresponds to pure absorption, while $\xi = 0$, when $\sigma_{\Ab} = 0$, corresponds to pure scattering.  
The equilibrium distribution function for neutrinos is given by the Fermi-Dirac distribution
\begin{equation}
  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}, 
  \label{eq:fermiDirac}
\end{equation}
where $T$ is the material temperature in energy units and $\mu$ is the neutrino chemical potential.
Both depend on the spatial position $\vect{x}$.

\subsection{Two-Moment Model}

Approximate solutions to the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by solving the two-moment model.
To this end, define the angular moments of the distribution function as follows
\begin{equation}
  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
  \label{eq:angularMoments}
\end{equation}
where $\vect{z}:=\{\varepsilon,\vect{x}\}$.  
The zeroth moment, $\cJ$, is referred to as the particle density.  
The first moment, $\bcH$, is the particle flux, and the second moment, $\bcK$, is proportional to the stress tensor.  
By integrating Eq.~\eqref{eq:boltzmann} over the momentum space angular dimension we obtain equations for the zeroth and the first moments
\begin{equation}
  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
  \label{eq:momentEquations}
\end{equation}
with $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, and
\begin{equation}
  \vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM},
  \label{eq:collisionTermMoments}
\end{equation}
where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$, $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, and
$\vect{I}$ is the identity matrix.
Hence, the process of solving the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, for the neutrino distribution function $f(\omega,\vect{z},t)$, is replaced by solving the two-moment equations for the neutrino number density, $\cJ(\vect{z},t)$, and flux, $\bcH(\vect{z},t)$.

\subsection{Algebraic Closures}

As is shown in the previous section, the moment equation for $\bcH$ involves the higher moment $\bcK$ and the two-moment model is open.  
To close the two-moment model, we consider algebraic closures.  
For the two-moment model, algebraic closures give an approximation to $\bcK$ using the lower moments.  
Write
\begin{equation}
  \bcK = \vect{k} \cJ,
\end{equation}
where $\vect{k}$ is the Eddington tensor.  
By assuming that the distribution function is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore~\cite{levermore_1984} proposed a simple form for the Eddington tensor
\begin{equation}
  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
  \label{eq:eddingtonTensor}
\end{equation}
where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.  
Thus, the two-moment model is closed by specifying the scalar $\chi$ in terms of $\cJ$ and $|\vect{\cH}|$.

\subsection{Constraints on the Moments}

Neutrinos are fermions and obey the Pauli exclusion principle.  
Because of this, the neutrino distribution function is bounded; i.e. $f \in [0,1]$.
As a result, the angular moments $\cJ$ and $\vect{\cH}$ and the Eddington factor $\chi$ satisfy the following bounds~\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}: 
\begin{align}
\cJ \in[0,1], \quad &(1-\cJ)\cJ-|\vect{\cH}| \geq 0, \label{eq:MomentsBounds} \\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  \leq & \chi \leq \min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
  \label{eq:eddingtonFactorBounds}
\end{align}
where $h = |\bcH|/\cJ$ is the flux factor.

The constraints in Eq.~\eqref{eq:MomentsBounds} define realizable moments $\bcM$.  
For fermions, realizable moments can only be constructed from a distribution satisfying the bounds $f \in [0,1]$.  
Moreover, the set of realizable moments is convex.  
As we will see later in Section~\ref{se:SpacialDiscretization}, this convexity makes it possible to design a constraint-preserving discretization for solving the two-moment model numerically.

The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve further attention.  
They are equally important, relative to those in Eq.~\eqref{eq:MomentsBounds}, in maintaining consistency of the two-moment model with respect to Fermi-Dirac statistics.  
When designing a numerical scheme for the two-moment model that maintains realizable $\bcM$, it is also necessary for the Eddington factor to satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.

However, recently reported CCSN simulations using two-moment neutrino transport with algebraic closures have employed Eddington factors that can violate the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
As examples, we consider the Eddington factors discussed in \cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies; $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} may work fine when the occupancy is low.  
When the occupancy is high, the Eddington factor due to these closures exceeds the upper bound for Fermi-Dirac statistics.  
The Eddington factor of Janka~1~\cite{janka_1991} may violate both the upper and lower bound on the Eddington factor.  
Only the closure due to Cernohorsky~\&~Bludman~\cite{cernohorskyBludman_1994} satisfies both the upper and lower bounds.  
This is not suprising as this is the only closure based on Fermi-Dirac statistics.  
Althought the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.  
When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.  
\ee{so what?  Should we discuss the presence of blocking factors in collision terms?}
%With those algebraic closures that don't conserve the bounds, the time integrator may give moments that implies $f>1$.
%Some safety protections may be applied for those method, but the safety protections can break the conservation laws in lepton number or energy and defect the CCSN simulation.

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupancy) and $\cJ=0.9$ (right panel, high occupancy).  In each panel we plot the Eddington factors of two-moment closures due to Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue), Janka~1 (purple), and Janka~2 (pink) .  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dashed black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}
